The Controlled Choice Design and Paternalism in Pawnshop Borrowing

### 2023-08-26 OA.tex
tot_tut_validity & edits to the main paper

\subsection{Survey}

\afterpage{
\begin{table}[H]
\caption{Baseline survey questions (translated to English)}
\label{baseline_survey}
\begin{center}
\scriptsize{\input{./Tables/transcribed.tex}}
\end{center}
\scriptsize
Translation of the baseline questionnaire.
\end{table}
}

@@

Panel A of this table presents the same information as Panel A of Table \ref{SS}, but restricts attention to the subsample of borrowers who answered \hl{at least one question???} in our baseline survey. Conditional on survey response, loan amount and weekday are balanced across treatment arms. Panel B presents response rates to each individual survey question across treatment arms, along with p-values for the F-test of no difference in response rates across survey arms. This panel uses data for borrowers who pawned on the \hl{same day as their survey response}.

@@

\begin{table}[H]
\caption{Multiple-loans robustness check}
\label{multiple_loans}
\begin{center}
\scriptsize{\input{./Tables/multiple_loans.tex}}
\end{center}
 \scriptsize
%\textit{Do file: } \texttt{multiple\_loans.do}
\end{table}

\todo[inline]{For Isaac to write the note.}
\end{landscape}

@@

\vspace{.2in}
\normalsize

Some loans in our sample are ``censored'' in that they continue beyond our observation period.
For these loans, we do not know whether the borrower ultimately defaulted our recovered her pawn.
In this appendix, we show that our main results are robust to different ways of addressing censoring.

Our main results, presented above, assumed that all loans that were still outstanding at the end of the sample period were \emph{eventually repaid}.
Because forced commitment causes borrowers to make payments earlier than they otherwise would have, this is a conservative assumption.
To see why, suppose for the sake of argument that commitment affects payment timing, but does not not default.
In other words, suppose that treatment makes censoring \emph{less likely} but has no effect on uncensored outcomes. 
If we were to treat all outstanding loans as defaults--the opposite of our convention--this would artificially inflate the rate of default among control loans relative to treatment loans. 
This is why we adopt the reverse convention above.
We now consider some alternative approaches.

\todo[inline]{@Frank: keep updating below after getting responses from @Issac.}

%The approach taken in the paper for censored loans is a conservative one in that it inherently assumes that all of the loans outstanding at the end of the observation window will be repaid, making it so that the acceleration of payment observed in the Forced arm does not translate mechanically into a treatment effect on default.  This appendix delves into it more detail.

One way of considering the effect that this issue could have on our results is to make extreme assumptions about the outcome of these loans in the treatment and control so as to bound the possible influence of censoring.  In Table \ref{bounding_censoring} we compare the Forced and Control arms, making the bracketing assumptions about repayment on censored loans.  Panel A assumes all censored loans are repaid, and Panel D that all default.  Panel B provides the lower bound for the treatment effect by assuming censored control loans are always repaid and treatment loans never are, and Panel C the upper bound by making the reverse assumption.  Comfortingly, even with these extreme assumptions the significance on the main treatment effects never flips and treatment effects on financial cost and interests payments remain negative and significant in all scenarios.  So there appears to be no scope for the censoring issue to overturn our main results.

Finally, Panel E of this table conducts a logit prediction model that uses all of the available information on loans that were completed to predict the outcome of loans that were not.  This is a best guess of the outcome on censored loans.  Using this prediction, we replicate the main experimental results and find that the treatment effect on financial cost increases from -378 (main results) to -525 (censored loans predicted), and the APR from -34\% to -62\%.  Hence, while the censoring issue does have a substantial influence on the magnitude of our estimated treatment effects, these  checks confirm that a) the core results are robust to censoring, and b) the headline approach that we take to the issue is conservative and is likely understating the true magnitude of impacts.

\vspace{.3in}
\begin{table}[H]
\caption{Bounding censoring} 
\label{bounding_censoring}
\begin{center}
\resizebox{0.9\textwidth}{!}{
\scriptsize{\input{./Tables/censoring_imp.tex}}
}
\end{center}
 \scriptsize 
 \todo[inline]{For Isaac to write the note}
%\textit{Do file: } \texttt{censoring_imp.do, censoring_imp_pr.do}
\end{table}

\begin{figure}[H]
        \caption{Interpolation on bounding censoring}
    \label{interpolation_censoring_imp}
    \begin{center}
   \begin{subfigure}{0.49\textwidth}
   \caption{Significance area for Default }
        \centering
        \includegraphics[width=\textwidth]{Figuras/frontera_sig_def_imp.pdf}
    \end{subfigure} 
   \begin{subfigure}{0.49\textwidth}
   \caption{Significance area for APR}
        \centering
        \includegraphics[width=\textwidth]{Figuras/frontera_sig_apr.pdf}
    \end{subfigure}     
    \end{center}
     \scriptsize  The next figure aims to answer the following question: For how many loans in the control arm can we impute recovery, and for how many in the treatment arm can we impute default and still have significance?
     This figure shows exactly the boundary separating significance when we vary the percentage of imputed censored loans with recovery and default respectively for control and treatment. Each corner in the square will correspond to one of the panels from the Table \ref{bounding_censoring}. For instance, the origin is the best-case scenario (Panel C) and the point (100,100) (Panel D) is the worst-case scenario. Thus we can think of this graph as an `interpolation' from the four extreme cases. The `x' indicates the proportions imputed by the lasso-logit model, and the different lines correspond to setting different significance levels.

     %\textit{Do file: }  \texttt{interpolation_{censoring_imp.do}
\end{figure}

@@

\begin{figure}[H]
        \caption{Financial benefit TUT effect for different discount rates}
    \label{fc_discount_rates}
    \begin{center}
        \centering
        \includegraphics[width=0.55\textwidth]{Figuras/discount_effect_tut.pdf}
    \end{center}
     \scriptsize This Figure re-estimates the treatment on the untreated (TUT) effect from Table \ref{tot_tut}, introducing a daily discount factor in the definition of financial benefit. The discount factor reflects time preference, i.e.\ the fact that payments made in the present are more costly for the borrower. At a given annual discount rate in percentage points (x-axis) the solid line gives the adjusted TUT and the shaded regions \hl{??? confidence intervals}. A discount factor of one corresponds to the estimate from Table \ref{tot_tut}. For higher discount rates, the adjusted financial cost will be higher, so the financial cost \emph{savings} will be lower. As seen from the figure, borrowers would need to face unrealistically large discount rates to reverse our headline result of a large, positive, and statistically significant TUT effect.
     %It estimates the effect of the treatment arms  for different discount factors, where a discount factor of 1 corresponds exactly to the estimate of column 1 of Table \ref{main_impact_table}. Because the commitment contract induces earlier payments, this adjusted financial cost will be higher, and thus financial savings will be lower. This figure shows the range of estimated effects and their confidence intervals, where the discount rate used is ploted in the x-axis annualized.    %\textit{Do file: }  \texttt{discounted\_noeffect.do}
\end{figure}

\vspace{.3in}
\subsection{Sure confidence and present bias}

\begin{figure}[H]
    \caption{Partition of TUT by behavioral variables.}
    \label{tut_beh_partition}
    \begin{center}
        \centering
        \includegraphics[width=0.55\textwidth]{Figuras/tut_beh_partition.pdf} 
    \end{center}
     \scriptsize  Each panel in this figure shows how the estimated treatment on the untreated (TUT) effect varies with a binary survey variable $X_i$. In the left panel (Sure-confidence) $X_i = 1$ if  borrower $i$ reported that she was certain to recover her pawn, zero otherwise. In the right panel (P.B.), $X_i = 1$ if borrower $i$ is ``present-biased'' based on her responses to the time preference questions from our survey. Each panel depicts three estimates and associated \hl{standard errors??? 95 CI?}: the overall TUT (blue), the TUT for borrowers with $X = 1$ (green), and the TUT for borrowers with $X = 0$ (red). By the law of iterated expectations, the overall TUT in each panel must lie between the group-specific TUTs. The overall TUT is slightly different in each panel, because some borrowers only completed part of the survey. In each panel, we present results for the full set of borrowers who answered the survey question or questions needed to determine $X_i$. From the right panel, we see that TUT does not appear to vary with present bias. In contrast, the left panel suggests that the positive and significant overall TUT is driven by individuals who are ``sure-confident,'' i.e.\ borrowers who report that they are certain to recover their pawn.
     %to be largely concentrated relevant survey question  according to her survey responses two binary performs a partition of the Treatment on the Untreated (FC), estimating the share of the effect that arises within each of two binary categories.  The top bars examine present bias (individuals are more impatient over one-month time horizon than they are between three and four months).  The bottom bars examine sure confidence (individual reports 100\% probability of repaying at time of taking loan).  Blue bar is the component arising from those without the trait, orange bar from those with the trait. 
      %\footnotesize{ \textit{Do file: }  \texttt{partition_tut.do}

      \todo[inline]{This figure has changed. Will have minor style modifications. @Issac: what's the purple stuff in the middle?}
\end{figure}

@@

    \begin{center}
       \begin{subfigure}{0.49\textwidth}
        \caption{APR}
        \centering
        \includegraphics[width=\textwidth]{Figuras/cdf_apr.pdf}
    \end{subfigure} 
   \begin{subfigure}{0.49\textwidth}
        \caption{Financial cost}
        \centering
        \includegraphics[width=\textwidth]{Figuras/cdf_fc_admin.pdf}
    \end{subfigure} 
    \end{center}
    \scriptsize This figure plots plots the empirical CDF of experimental outcomes separately for the control / status quo (dashed) and forced commitment contracts (solid). In panel (a), the outcome is APR; in panel (b) the outcome is Financial Cost. In each case, the empirical CDF under forced commitment first-order stochastically dominates the empirical CDF under the status quo. This can be seen by examining the dotted line at the bottom of panels (a) and (b), which shows the difference $(\text{Control} - \text{Commitment})$. 
    %The dotted line at the bottom of panels (a) and (b)   the empirical cumulative distribution function APR and financial cost of financial cost. It does this separately for the fee-forcing contract and for the status-quo contract. The dotted line at the bottom is the difference of the control CDF minus the forced CDF arm. It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line).
    % \texttt{fosd_ecdf.do}}
\end{figure}

@@

%Are we using any tables/figures after this point?

@@

We operationalize this idea using a two-step approach proposed by \cite{chernozhukov2018generic}.  We begin by randomly dividing the participants in the forced arms of the experiment ($Z_i \neq 2$) into two groups: a training set and a test set.
These sets are constructed to ensure that all observations from a given branch-day cluster are allocated to the same set.
This avoids inferential problems that could arise from correlated unobservables within clusters.
In the first step, we apply the generalized random forest approach of \cite{athey2019generalized} to the training set to estimate two proxy predictors: $\psi(\cdot|\text{Training})$ approximates the untreated potential outcome function, $\mathbbm{E}[Y_{i0}|X_i] = \mathbbm{E}[Y_i|Z_i=0,X_i]$, while  $\tau(\cdot|\text{Training})$, approximates the ATE function
\[
\text{ATE}(X_i) = \mathbbm{E}[Y_i|Z_i=1,X_i] - \mathbbm{E}[Y_i|Z_i=0, X_i].
\]
The proxy predictors need not be unbiased or even consistent estimators of the functions they aim to approximate: the goal of this exercise is merely to find a scalar function of $X_i$ that \emph{accurately predicts} $\text{ATE}(X_i)$.
In the second step we fit a linear regression model to data from the training set using regressors constructed from the proxy functions $\psi(\cdot|\text{Training})$ and $\tau(\cdot|\text{Training})$ constructed in the first step. In particular, we estimate 
\begin{equation}
Y_i = \alpha_0 + \alpha_1 \psi_i + \beta_1 (Z_i - \mathbbm{E}[Z_i]) + \beta_2 (Z_i - \mathbbm{E}[Z_i])(\tau_i - \mathbbm{E}[\tau_i]) + \epsilon_i
\label{eq:chernreg}
\end{equation}
where $\psi_i \equiv \psi(X_i|\text{Training})$ and $\tau_i \equiv \tau(X_i|\text{Training})$.\footnote{This is a slightly simpler regression than the one proposed in equation (3.1) of \cite{chernozhukov2018generic}, which involves propensity score weights. Because the random assignment of $Z$ in our experiment does \emph{not} condition on $X$, the propensity score weights in our case are constant over $X$ and hence drop out.} As shown by \cite{chernozhukov2018generic}, the coefficients $\beta_1$ and $\beta_2$ from \eqref{eq:chernreg} identify the \emph{best linear predictor} of the conditional ATE based on $\tau(\cdot|\text{Training})$, namely
\[
\beta_1 = \mathbbm{E}[\text{ATE}(X_i)] = \text{ATE}, \quad
\beta_2 = \frac{\text{Cov}[\text{ATE}(X_i), \tau_i]}{\text{Var}(\tau_i)}.
\]
If treatment effects are homogeneous we must have $\beta_2 = 0$. Rejecting this hypothesis establishes that $\tau_i$ predicts $\text{ATE}(X_i)$ and hence that $\Delta_i$ varies. 
Since $\tau_i$ and $\psi_i$ do not depend on the test set, inference for the regression in \eqref{eq:chernreg} is straightforward conditional on the Training/Test split.  
Our estimate for $\beta_2$ is \hl{XXXX} with a cluster-robust standard error of \hl{XXXX}.
Thus we easily reject the null hypothesis of homogenous treatment effects.

@@

\subsection{Inference for ASG, ASB, and ASL}
We now explain how to carry out cluster-robust inference for the ASG, ASB, and ASL effects, as implemented in our companion STATA package.
Each of these effects can be expressed as a difference of coefficients from two just-identified linear IV regressions.
The ASG effect is the difference of the \text{TOT} effect from Proposition \ref{prop:TOTreg} and the \text{TUT} effect from Proposition \ref{prop:TUTreg}.
Similarly, the ASB effect is the difference of $\mathbb{E}(Y_0|C=1)$ and $\mathbbm{E}(Y_0|C=0)$ from Proposition \ref{prop:ASBreg} while the ASL effect is the difference of $\mathbbm{E}(Y_1|C=1)$ and $\mathbbm{E}(Y_1|C=0)$ from Proposition \ref{prop:ASLreg}.
Within each pair of IV regressions the outcome variable and instrument set is identical; only the regressors differ. 
Since our estimators of all three effects share the same structure, our discussion of inference abstracts from the specific regressors and instruments used in each case to avoid duplication. 
To implement these results in practice without relying on our STATA package, simply substitute supply the regressors and instruments specified in the relevant propositions.

@@

\todo[inline]{@Issac: Presumably the numerical results and sentence that follows it need to be updated now that we've changed how we deal with censoring etc, yes? Which outcome are we looking at here} 
The \cite{huber_mellace} bounds for the TOT \& TUT APR are respectively:
\[\text{TOT} : [-481.8, 483.7]\quad\quad\quad\text{TUT} : [-17.9, 90.6]\]

Because the Note that since both TUT and ToT estimates from the LATE approach lies inside these bounds, we do not falsify the exclusion restriction.

@@

\begin{figure}[H]
     \caption{Exclusion restriction}
     \label{exclusion_restriction}
    \begin{center}
    \begin{subfigure}{0.6\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/exclusion_restriction.pdf}
    \end{subfigure}
    \end{center}
    \scriptsize This figure serves as a test for the exclusion restriction in the point identification for the TOT and the TUT. It shows the effect on the effective cost/loan ratio for the forced-fee arm and the choice arm, together with the decomposition of the choosers and non-choosers. Note that a) being forced into the treatment (Forced fee) has the same effect as choosing it (Choosers), and b) not choosing the treatment (Non chooser) has no effect with respect to the control.

>>>>

\newpage
\subsection{Survey}   \label{app:survey_data}

\vspace{.2in}

We now present analysis of the extent to which the survey-responding sample is representative and balanced.
Table \ref{SS_cond_survet} presents information about survey non-response.
Panel A is a balance table that compares loan amount and day of the week across treatment arms for the subset of borrowers who responded to at least one survey question.
The p-values in the fourth column are for the F-test of no difference of means across treatment arms. 
Panel B presents response-rates by question for each arm of the experiment, along with p-values for the F-test of no difference in question-specific response rates across treatment arms. 
This panel uses data from participants who answered at least one survey question and went on to pawn on the same day as their survey response.
From the table, we see that loan amount and weekday are balanced across treatment arms among survey respondents and that response rates are likewise stable across treatment arms.
Table \ref{TUT_cond_survet} shows how the estimated TUT effect changes if we restrict our estimation sample based on survey response.
The first row of the table presents TUT results for the financial cost outcome, while the second presents corresponding results for the APR outcome.
In each row, column (1) presents the full-sample TUT estimate and standard error while the remaining columns restrict the sample to borrowers who answered a particular survey question or set of questions.
For example, column (4) presents results for borrowers who answered the two questions needed to compute our measure of ``present bias'' discussed in the next paragraph, while column (9) present results restricted to participants who disclosed their sex. 
As seen from the table, our TUT estimates are quite stable across sub-samples defined by survey response.
In each case they are positive and of the same magnitude as the corresponding full-sample estimate, although statistical significance varies depending on the size of the corresponding sub-sample. 
For these reasons, we are comfortable relying on data for survey respondents in the empirical exercises that follow.
In exercises that rely on a single survey question, we use data for every borrower who answered that question.
In the random forest exercises described below, we use data for every borrower who answered at least one survey question.

\begin{table}[H]
\caption{Baseline survey questions (translated to English)}
\label{baseline_survey}
\begin{center}
\scriptsize{\input{./Tables/transcribed.tex}}
\end{center}
\scriptsize
Translation of the baseline questionnaire.
\end{table}

@@

Panel A of this table presents the same information as Panel A of Table \ref{SS}, but restricts attention to the subsample of borrowers who answered at least one question in our baseline survey. Conditional on survey response, loan amount and weekday are balanced across treatment arms. Panel B presents response rates to each individual survey question across treatment arms, along with p-values for the F-test of no difference in response rates across survey arms. This panel uses data for borrowers who pawned on the same day as their survey response.

@@

\begin{table}[H]
\caption{Multiple-loans robustness check}
\label{multiple_loans}
\begin{center}
\scriptsize{\input{./Tables/multiple_loans.tex}}
\end{center}
 \scriptsize
 An additional empirical issue generated by repeat pawning is the question of how to handle the treatment status of those who take multiple loans within the experiment.  43\% of borrowers take more than one loan within the study period, and 19\% are assigned multiple treatment statuses on their different loans.  The issue of sequential endogenous treatments has been extensively studied in the context of school lotteries, where the convention is to use the treatment status from the first exposure (ITT) \citep{cullen2006effect, abdulkadirouglu2011accountability}.\\

 This table provides robustness for our main results for different ways to handling the multiplicity of loans. Columns 1-4 repeat the main analysis of financial cost and APR using the baseline approach from our main results,i.e. it only considers the first visit, while allowing multiple loans for the same-day. Columns 5-8 considers all loans including dummies for the order of pawns for an individual, essentially making the identification within-order.  Columns 9-12 pursue the ITT strategy of always assigning the first treatment status to all subsequent pawns. The core treatment effects are robust to any of these ways of handling repeat pawning.

%\textit{Do file: } \texttt{multiple\_loans.do}
\end{table}

\end{landscape}

\begin{figure}[H]
    \caption{Determinants of choice}
    \label{determinants_choose}
    \begin{center}
    \begin{subfigure}{0.75\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/determinants_choose_commitment.pdf}
    \end{subfigure}
    \end{center}
      \scriptsize

      The above figure shows the determinants in a bivariate and multivariate OLS regression of choosing commitment. Choice commitment is a binary variable equal to one, whenever subjects choose the forced commitment contract in the choice arm. 
%\textit{Do file: } \texttt{determinants_choice_sure_confidence.do}       
\end{figure}

\vspace{.2in}
\begin{figure}[H]
    \caption{Histogram of payments}
    \label{hist_payments}
    \begin{center}
    \begin{subfigure}{0.45\textwidth}
        \caption{Status-quo}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_payments_sq.pdf}
    \end{subfigure}
    \begin{subfigure}{0.45\textwidth}
        \caption{Forced commitment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_payments_fc.pdf}
    \end{subfigure}
    \begin{subfigure}{0.45\textwidth}
        \caption{Choice commitment}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_payments_cc.pdf}
    \end{subfigure}    
    \end{center}
     \scriptsize
     This figure shows the schedule of payments for each treatment arm. In other words it records the time after the loan origination when the borrower makes a payment toward recovery of the pawn. We can see that for both the Forced commitment and Choice commitment arm, payments are bunching at the 30 and 60 days, while most payments are done around the due date of the loan (90 days).

      %\footnotesize{ \textit{Do file: }  \texttt{hist\_payments.do}}
\end{figure}

@@

\vspace{.2in}

Some loans in our sample are ``censored'' in that they continue beyond our observation period.
For these loans, we do not know whether the borrower ultimately defaulted or recovered her pawn.
In this appendix, we show that our main results are robust to different ways of addressing censoring.

Our main results, presented above, make no assumption on the default/recovery status of this loans. However, we compute the Financial Cost \& APR considering all the payments done so far. We now consider some alternative approaches. \\

One way of considering the effect that this issue could have on our results is to make extreme assumptions about the outcome of these loans in the treatment and control so as to bound the possible influence of censoring.  In Table \ref{bounding_censoring} we compare the Forced and Control arms, making the bracketing assumptions about repayment on censored loans.  Panel A assumes all censored loans are repaid, and Panel D that all default. Because forced commitment causes borrowers to make payments earlier than they otherwise would have, In Panel A we make a conservative assumption. To see why, suppose for the sake of argument that commitment affects payment timing, but does not not default.
In other words, suppose that treatment makes censoring \emph{less likely} but has no effect on uncensored outcomes. 
If we were to treat all outstanding loans as defaults--the opposite of our convention--this would artificially inflate the rate of default among control loans relative to treatment loans.

Panel B provides the lower bound for the treatment effect by assuming censored control loans are always repaid and treatment loans never are, and Panel C the upper bound by making the reverse assumption.  Comfortingly, even with these extreme assumptions the significance on the main treatment effects never flips and treatment effects on financial cost and interests payments remain negative and significant in all scenarios.  So there appears to be no scope for the censoring issue to overturn our main results.

Finally, Panel E of this table conducts a lasso logit prediction model that uses all of the available information on loans that were completed to predict the outcome of loans that were not.  This is a best guess of the outcome on censored loans.  Using this prediction, we replicate the main experimental results and find that the treatment effect on financial cost increases from -378 (main results) to -530 (censored loans predicted), and the APR from -34\% to -62\%.  Hence, while the censoring issue does have a substantial influence on the magnitude of our estimated treatment effects, these  checks confirm that a) the core results are robust to censoring, and b) the headline approach that we take to the issue is conservative and is likely understating the true magnitude of impacts.

\vspace{.3in}
\begin{table}[H]
\caption{Bounding censoring} 
\label{bounding_censoring}
\begin{center}
\resizebox{0.9\textwidth}{!}{
\scriptsize{\input{./Tables/censoring_imp.tex}}
}
\end{center}

\end{table}
 \scriptsize 
 Given the censored loans, i.e. loans that have not finished by the end of the observation period, we estimate `a la Manski' bounds for these loans, meaning that we impute all loans to either \emph{default}$=1$ or \emph{recovery}$=0$ depending on the treatment arm. Different panels perform different imputations for the censored loans for all possible combinations for the imputation, and computes the ATE for the same outcomes of Table \ref{main_impact_table}. Panel A, for instance, assumes that all outstanding loans are fully payed. Panel B is the most conservative imputation since it assumes all outstanding loans in the control arm are payed, while all the outstanding loans in the forced commitment arm default. Panel C, on the other hand, is the most optimistic scenario opposite to that of Panel B. Panel D assumes all remaining loans default. The last panel makes the imputation to the censored loans according to the best prediction using a piecewise lasso logit model for default. In concrete, we build two logit models with lasso regularization, depending whether the loan duration is less than 220 days (two cycles) or more than 220 days. For prediction we use the former whenever the last recorded payment was done within 220 days, and the latter otherwise. Both models includes loan characteristics (loan size, branch), and payment behavior (loan duration so far, days to first payment, \% of first payment, \% of payments at 30, 60, 90, and 105 days, and \% of interest payed at 105 days), but the latter model also includes \% of payments at 150, 180, and 210 days. This predictive model achieves an accuracy rate of 92\% both in-sample and out-of-sample.

 Note that in all panels we maintain significant results for Financial Cost as dependent variable, while only in the most conservative scenario (Panel B) we lose significance for the APR outcome.

\begin{figure}[H]
        \caption{Interpolation on bounding censoring}
    \label{interpolation_censoring_imp}
    \begin{center}
   \begin{subfigure}{0.49\textwidth}
   \caption{Significance area for APR}
        \centering
        \includegraphics[width=\textwidth]{Figuras/frontera_sig_apr.pdf}
    \end{subfigure}     
    \begin{subfigure}{0.49\textwidth}
   \caption{Significance area for Default }
        \centering
        \includegraphics[width=\textwidth]{Figuras/frontera_sig_def_imp.pdf}
    \end{subfigure} 
    \end{center}
     \scriptsize  The next figure aims to answer the following question: For how many loans in the control arm can we impute recovery, and for how many in the treatment arm can we impute default and still have significance?
     This figure shows exactly the boundary separating significance when we vary the percentage of imputed censored loans with recovery and default respectively for control and treatment. Each corner in the square will correspond to one of the panels from the Table \ref{bounding_censoring}. For instance, the origin is the best-case scenario (Panel C) and the point (100,100) (Panel B) is the worst-case scenario. Thus we can think of this graph as an `interpolation' from the four extreme cases. The `x' indicates the proportions imputed by the lasso logit model, and the different lines correspond to setting different significance levels. We do not include the plot for financial cost, since for any imputation we still have significant results.

     %\textit{Do file: }  \texttt{interpolation_censoring_imp.do}
\end{figure}

@@

\begin{figure}[H]
        \caption{Financial benefit TUT effect for different discount rates}
    \label{fc_discount_rates}
    \begin{center}
        \centering
        \includegraphics[width=0.55\textwidth]{Figuras/discount_effect_tut.pdf}
    \end{center}
     \scriptsize This Figure re-estimates the treatment on the untreated (TUT) effect from Table \ref{tot_tut}, introducing a daily discount factor in the definition of financial benefit. The discount factor reflects time preference, i.e.\ the fact that payments made in the present are more costly for the borrower. At a given annual discount rate in percentage points (x-axis) the solid line gives the adjusted TUT and the shaded regions 90\% \& 95\% confidence bands. A discount factor of one corresponds to the estimate from Table \ref{tot_tut}. For higher discount rates, the adjusted financial cost will be higher, so the financial cost \emph{savings} will be lower. As seen from the figure, borrowers would need to face unrealistically large discount rates to reverse our headline result of a large, positive, and statistically significant TUT effect.
     %It estimates the effect of the treatment arms  for different discount factors, where a discount factor of 1 corresponds exactly to the estimate of column 1 of Table \ref{main_impact_table}. Because the commitment contract induces earlier payments, this adjusted financial cost will be higher, and thus financial savings will be lower. This figure shows the range of estimated effects and their confidence intervals, where the discount rate used is ploted in the x-axis annualized.    %\textit{Do file: }  \texttt{discounted\_noeffect.do}
\end{figure}

@@

    \begin{center}
       \begin{subfigure}{0.49\textwidth}
        \caption{APR benefit}
        \centering
        \includegraphics[width=\textwidth]{Figuras/cdf_apr.pdf}
    \end{subfigure} 
   \begin{subfigure}{0.49\textwidth}
        \caption{Financial benefit}
        \centering
        \includegraphics[width=\textwidth]{Figuras/cdf_fc_admin.pdf}
    \end{subfigure} 
    \end{center}
    \scriptsize This figure plots plots the empirical CDF of experimental outcomes separately for the control / status quo (dashed) and forced commitment contracts (solid). In panel (a), the outcome is APR benefit; in panel (b) the outcome is Financial benefit. In each case, the empirical CDF under forced commitment first-order stochastically dominates the empirical CDF under the status quo. This can be seen by examining the dotted line at the bottom of panels (a) and (b), which shows the difference $(\text{Control} - \text{Commitment})$. 
    %The dotted line at the bottom of panels (a) and (b)   the empirical cumulative distribution function APR and financial cost of financial cost. It does this separately for the fee-forcing contract and for the status-quo contract. The dotted line at the bottom is the difference of the control CDF minus the forced CDF arm. It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line).
    % \texttt{fosd_ecdf.do}}
\end{figure}

\begin{figure}[H]
        \caption{Distribution of treatment effects under rank invariance.}
    \label{te_rankinvariance}

    \begin{center}
       \begin{subfigure}{0.49\textwidth}
        \caption{APR benefit}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_rankinvariance_apr.pdf}
    \end{subfigure} 
   \begin{subfigure}{0.49\textwidth}
        \caption{Financial benefit}
        \centering
        \includegraphics[width=\textwidth]{Figuras/te_rankinvariance_fc_admin.pdf}
    \end{subfigure} 
    \end{center}
    \scriptsize This figure show the distribution of treatment effects under rank invariance
    \[F_\Delta(\delta) = \int_0^1 \mathbbm{1}\{ F_1^{-1}(u) - F_0^{-1}(u)\leq \delta\}\,\mathrm{d}u\]
where $F_1^{-1}$ and $F_0^{-1}$ are the quantile functions of $Y_1$ and $Y_0$.
    %The dotted line at the bottom of panels (a) and (b)   the empirical cumulative distribution function APR and financial cost of financial cost. It does this separately for the fee-forcing contract and for the status-quo contract. The dotted line at the bottom is the difference of the control CDF minus the forced CDF arm. It shows that the CDF of the status quo contract is always below that of the fee-forcing (and this difference is significant for the points indicated by the blue line).
    % \texttt{fosd_ecdf.do}}
\end{figure}

@@

\begin{figure}[H]
    \caption{Determinants sure confidence}
    \label{determinants_sure}
    \begin{center}
    \begin{subfigure}{0.75\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/determinants_confidence_100.pdf}
    \end{subfigure}
    \end{center}
      \scriptsize

      The above figure shows the determinants in a bivariate and multivariate OLS regression of sure confidence among the non-choosers. Sure confidence is a binary variable defined to be one when people report a 100\% probability of recovery.
%\textit{Do file: } \texttt{determinants_choice_sure_confidence.do}       
\end{figure}

@@

We operationalize this idea using a two-step approach proposed by \cite{chernozhukov2018generic}.  We begin by randomly dividing the participants in the forced arms of the experiment ($Z_i \neq 2$) into two groups: a training set and a test set.
These sets are constructed to ensure that all observations from a given branch-day cluster are allocated to the same set.
This avoids inferential problems that could arise from correlated unobservables within clusters.
In the first step, we apply the generalized random forest approach of \cite{atheygrf} to the training set to estimate two proxy predictors: $\psi(\cdot|\text{Training})$ approximates the untreated potential outcome function, $\mathbbm{E}[Y_{i0}|X_i] = \mathbbm{E}[Y_i|Z_i=0,X_i]$, while  $\tau(\cdot|\text{Training})$, approximates the ATE function
\[
\text{ATE}(X_i) = \mathbbm{E}[Y_i|Z_i=1,X_i] - \mathbbm{E}[Y_i|Z_i=0, X_i].
\]
The proxy predictors need not be unbiased or even consistent estimators of the functions they aim to approximate: the goal of this exercise is merely to find a scalar function of $X_i$ that \emph{accurately predicts} $\text{ATE}(X_i)$.
In the second step we fit a linear regression model to data from the training set using regressors constructed from the proxy functions $\psi(\cdot|\text{Training})$ and $\tau(\cdot|\text{Training})$ constructed in the first step. In particular, we estimate 
\begin{equation}
Y_i = \alpha_0 + \alpha_1 \psi_i + \beta_1 (Z_i - \mathbbm{E}[Z_i]) + \beta_2 (Z_i - \mathbbm{E}[Z_i])(\tau_i - \mathbbm{E}[\tau_i]) + \epsilon_i
\label{eq:chernreg}
\end{equation}
where $\psi_i \equiv \psi(X_i|\text{Training})$ and $\tau_i \equiv \tau(X_i|\text{Training})$.\footnote{This is a slightly simpler regression than the one proposed in equation (3.1) of \cite{chernozhukov2018generic}, which involves propensity score weights. Because the random assignment of $Z$ in our experiment does \emph{not} condition on $X$, the propensity score weights in our case are constant over $X$ and hence drop out.} As shown by \cite{chernozhukov2018generic}, the coefficients $\beta_1$ and $\beta_2$ from \eqref{eq:chernreg} identify the \emph{best linear predictor} of the conditional ATE based on $\tau(\cdot|\text{Training})$, namely
\[
\beta_1 = \mathbbm{E}[\text{ATE}(X_i)] = \text{ATE}, \quad
\beta_2 = \frac{\text{Cov}[\text{ATE}(X_i), \tau_i]}{\text{Var}(\tau_i)}.
\]
If treatment effects are homogeneous we must have $\beta_2 = 0$. Rejecting this hypothesis establishes that $\tau_i$ predicts $\text{ATE}(X_i)$ and hence that $\Delta_i$ varies. 
Since $\tau_i$ and $\psi_i$ do not depend on the test set, inference for the regression in \eqref{eq:chernreg} is straightforward conditional on the Training/Test split.  
Our estimate for $\beta_2$ is 1.68 with a one-sided heteroskedasticity-robust (HC3) of 0.50.
Thus we easily reject the null hypothesis of homogeneous treatment effects.

@@

\subsection{Inference for ASG, ASB, and ASL}
\label{subsec:inference}
We now explain how to carry out cluster-robust inference for the ASG, ASB, and ASL effects, as implemented in our companion STATA package.
Each of these effects can be expressed as a difference of coefficients from two just-identified linear IV regressions.
The ASG effect is the difference of the \text{TOT} effect from Proposition \ref{prop:TOTreg} and the \text{TUT} effect from Proposition \ref{prop:TUTreg}.
Similarly, the ASB effect is the difference of $\mathbb{E}(Y_0|C=1)$ and $\mathbbm{E}(Y_0|C=0)$ from Proposition \ref{prop:ASBreg} while the ASL effect is the difference of $\mathbbm{E}(Y_1|C=1)$ and $\mathbbm{E}(Y_1|C=0)$ from Proposition \ref{prop:ASLreg}.
Within each pair of IV regressions the outcome variable and instrument set is identical; only the regressors differ. 
Since our estimators of all three effects share the same structure, our discussion of inference abstracts from the specific regressors and instruments used in each case to avoid duplication. 
To implement these results in practice without relying on our STATA package, simply substitute supply the regressors and instruments specified in the relevant propositions.

@@

\todo[inline]{Add exercise about falsification of exclusion that Frank suggested.}
The \cite{huber_mellace} bounds for the TOT \& TUT APR are respectively:
\[\text{TOT} : [-366, 490]\quad\quad\quad\text{TUT} : [-19, 109]\]

Since both TUT (24) and ToT (121) estimates from the LATE approach lies inside these bounds, we cannot falsify the exclusion restriction.

@@

% \begin{figure}[H]
%      \caption{Exclusion restriction}
%      \label{exclusion_restriction}
%     \begin{center}
%     \begin{subfigure}{0.6\textwidth}
%         \centering
%         \includegraphics[width=\textwidth]{Figuras/exclusion_restriction.pdf}
%     \end{subfigure}
%     \end{center}
%     \scriptsize This figure serves as a test for the exclusion restriction in the point identification for the TOT and the TUT. It shows the effect on the effective cost/loan ratio for the forced-fee arm and the choice arm, together with the decomposition of the choosers and non-choosers. Note that a) being forced into the treatment (Forced fee) has the same effect as choosing it (Choosers), and b) not choosing the treatment (Non chooser) has no effect with respect to the control.

%           %\footnotesize{ \textit{Do file: }  \texttt{exclusion\_restriction.do}}
% \end{figure}
